---
title: "R Notebook"
output: html_notebook
---

```{r}
install.packages("tidytext")
```

```{r}
library(tidytext)
sentiments
```

```{r}
get_sentiments("bing")
```

```{r}
library(janeaustenr)
library(stringr)
library(tidytext)
library(dplyr)
```

```{r}

tidy_data <- austen_books() %>%
 group_by(book) %>%
 mutate(linenumber = row_number(),
   chapter = cumsum(str_detect(text, regex("^chapter [\\divxlc]", 
                          ignore_case = TRUE)))) %>%
ungroup() %>%
unnest_tokens(word, text)

```


```{r}
positive_senti <- get_sentiments("bing") %>%
 filter(sentiment == "positive")

tidy_data %>%
 filter(book == "Emma") %>%
 semi_join(positive_senti) %>%
 count(word, sort = TRUE)
```

```{r}
install.packages("tidyr")
```

```{r}
library(tidyr)
bing <- get_sentiments("bing")
Emma_sentiment <- tidy_data %>%
 inner_join(bing) %>%
 count(book = "Emma" , index = linenumber %/% 80, sentiment) %>%
 spread(sentiment, n, fill = 0) %>%
 mutate(sentiment = positive - negative)
```
```{r}
install.packages("ggplot2")
```

```{r}
library(ggplot2)

ggplot(Emma_sentiment, aes(index, sentiment, fill = book)) +
 geom_bar(stat = "identity", show.legend = TRUE) +
 facet_wrap(~book, ncol = 2, scales = "free_x")
```

```{r}
counting_words <- tidy_data %>%
 inner_join(bing) %>%
 count(word, sentiment, sort = TRUE)
head(counting_words)
```

```{r}
counting_words %>%
 filter(n > 150) %>%
 mutate(n = ifelse(sentiment == "negative", -n, n)) %>%
 mutate(word = reorder(word, n)) %>%
 ggplot(aes(word, n, fill = sentiment))+
 geom_col() +
 coord_flip() +
 labs(y = "Sentiment Score")
```

```{r}
install.packages("reshape2")
install.packages("wordcloud")
```

```{r}
library(reshape2)
library(wordcloud)
tidy_data %>%
 inner_join(bing) %>%
 count(word, sentiment, sort = TRUE) %>%
 acast(word ~ sentiment, value.var = "n", fill = 0) %>%
 comparison.cloud(colors = c("red", "dark green"),
          max.words = 100)
```

```{r}

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
